Modal Abstractions for Virtualizing Memory Addresses

### 2025-07-30 programlogic.tex
the magic of sed (i.e., replacing all the mathcal I with regular math mode I)

  \begin{figure*}
  \footnotesize
\vspace{-1em}
\centerline{$
\begin{array}{l}
  \mathcal{I}\textsf{ASpace}(\ptablestore,m)\stackrel{\triangle}{=} \textsf{ASpace\_Lookup}(\ptablestore,m) \ast 
  \bigast{(\vaddr, \textsf{pa})\in \ptablestore}{\exists\;(\textsf{l4e l3e l2e, l1e, pa})\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\vaddr\textsf{, l4e, l3e, l2e, l1e, pa})} \\
  \textsf{ where } 
   \textsf{ASpace\_Lookup} (\ptablestore,m) \stackrel{\triangle}{=} \lambda\textsf{ cr3val} \ldotp \; \exists \gammaPred \; \ldotp \ulcorner m \; !!\; \textsf{cr3val} = \textsf{Some } \gammaPred \urcorner \ast
    %\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}
    \ptableabswalk{\delta,\theta}
\end{array}
$}
\vspace{-1em}
\caption{Per-address-space invariant with a fixed global map of address space names $m$}
  \label{fig:peraspaceinvariant}
\vspace{-1em}
  \end{figure*}

We place the authorative ownership of the ghost \add{map} translation $\mathcal{A}\textsf{PTableWalk}$ in a per-address-space invariant
$\mathcal{I}$\textsf{ASpace} (Figure \ref{fig:peraspaceinvariant}), 
\replace{$\mathcal{I}$\textsf{ASpace} alone allows}{allowing} changes to the page tables
that preserve overall virtual-to-physical translations \add{in isolation},
\add{and also allowing changes to specific the virtual-to-physical translations}
\replace{W}{w}hen combined with the
\replace{fragment}{token} stored in the \add{relevant} virtual points-to (Figure \ref{fig:virtualpointstosharing}).
\del{changes in the virtual-to-physical translations become possible without the need to track all virtual points-to assertions.}
\looseness=-1

% \todo[inline,color=cyan]{Explain $\delta{s}$ (Iris ghost name) vs $m$ (logical contents of ghost map) in next 2 paragraphs}
% \todo[inline]{This next paragraph below explains details, but should first explain the big picture: the current address space
% is identified by a paddr, so to state the invariant for the address space named by that paddr we need to look up
% what invariants should hold, then assert that those invariants do hold.}
\add{We must also ensure that different address spaces can have independent ghost maps ---
which we resolve with an additional unique global ghost map (with ghost name $\delta{s}$) from address-space identifiers (page table roots
whose values are manipulated by the kernel code) to
the \textsc{Iris} ghost name for that address space's ghost map.
In Figure \ref{fig:virtualpointstosharing}, the extra ghost map token for $\delta{s}$ asserts that $\delta$ --- which is exisentially
quantified --- is the correct ghost name for the current address space. That is then the ghost map named
in the ghost virtual-to-physical translation token of Figure \ref{fig:virtualpointstosharing}.
}
\del{In Figure ??,
$\theta$ is the logical map from virtual addresses to the physical addresses they should translate to, 
for the \emph{current} address space, corresponding to the  currently installed page tables (the ones
indicated by \texttt{cr3}). In Figure ??, the existentially quantified $\delta$
is the ghost name for this map (again, for the current address space).
Because our logic is the first to address the existence of multiple address spaces,
it must ensure that $\theta$ actually corresponds to the intended ghost map for the current address space.
This requires looking up the ghost name (i.e., $\delta$) for the current address space,
which is handled by $m$ --- another logical map (tied to ghost state shortly)
from various page table roots to ghost names for the per-address-space ghost maps discussed above.
}
\add{
Just as the ghost name $\delta$ names the ghost map with contents $\theta$,
$\delta{s}$ names a ghost map, whose contents appear as $m$ in Figure \ref{fig:peraspaceinvariant} (the association of $\delta{s}$ to $m$
is a global invariant not shown).
}
$\mathcal{I}\textsf{ASpace}(\theta,m)$ then \add{performs 3 roles:
it associates the current address space's root with an appropriate \textsc{Iris} ghost name $\delta$;
it tracks authoritatively that $\delta$'s logical contents match $\theta$; and it}
stores the physical resources for the current address space mappings \add{(via the iterated $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$)}.
\del{ensuring that the current address space is valid (has an entry in $m$ whose corresponding
authoritative map matches $\theta$), and asserting ownership of the appropriate fractional ownership
of the physical page table walk for each virtual-to-physical translation in $\Theta$ (for the current address space).}

@@

% Figure \ref{fig:logicaladdrspace} depicts the relationships between these pieces, for a single
% address space.
% The invariant for the currently active address space (solid round square labelled as 
% $\mathcal{I}$\textsf{ASpace} in Figure \ref{fig:logicaladdrspace}) asserts authorative ownership (i.e. 
% update capability), $\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$, of the ghost map $\Theta$
% describing virtual-to-physical address translations
% -- shown as a solid-round-head arrow to $\mathcal{A}\textsf{PTableWalk}$.
% Each virtual points-to assertion (dashed round square labelled as \textsf{Virtual PointsTo}
%  in Figure \ref{fig:peraspaceinvariant})
% asserts fragmental ownership of the ghost map $\Theta$, $\sumwalkabs\vaddr\qfrac\paddr$,
% shown via the dashed-diamond-head arrow to $\mathcal{A}\textsf{PTableWalk}$. Specifically, it asserts that
% the virtual address the virtual points-to assertion concerns corresponds to some physical address.
% There exists only one persistent authorative ownership 
% ($\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$) which collects the fragmental 
% ghost page-table-walk mapping ($\sumwalkabs\vaddr\qfrac\paddr$),
%  shown as double-ended solid arrow 1 to N imposing the update protocol.

@@

% \paragraph{From A Single Address Space to Many}
% In principle the resources from each individual address space should be collected into a single
% shared invariant, and for each memory access,
% a fragment of this corresponding to $\mathcal{I}\textsf{ASpace}(\Theta,m)$
% for the current address space should be extracted from this global resource, used to prove correctness of the
% memory access, and put back.
% In this paper we focus on the middle section, explicity identifying resources for each
% address space. The reason for this is that in practice, this global resource is also
% the place where kernel-specific assumptions, such as guaranteeing that certain virtual address range
% was mapped in all address spaces, would be enforced. This paper focuses on the
% reasoning principles behind the virtual memory access, and we leave the use of this within a larger
% kernel to future work. We do, however, deal with the existence of multiple address spaces in examples (Section \ref{sec:experiment}).

@@

    P \ast \mathcal{I}\textsf{ASpace}\ast  \textsf{rip} \mapsto_{\textsf{r}} \; {\textsf{iv} + \textsf{MovLen}(\textsf{r}_d,[\textsf{r}_a])} \ast \arcr

@@

  \{P \ast \mathcal{I}\textsf{ASpace}\ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{ iv} \ast r_d \mapsto_{r}  \textsf{ rvd} \ast r_a \mapsto_{r} \;\{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{ v} \}_{\textsf{rtv}}\;

@@

  \{P \ast \mathcal{I}\textsf{ASpace}\ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{ iv} + \textsf{MovLen}(\textsf{r}_d,[\textsf{r}_a])  \ast r_s \mapsto_{r}\;\{q_1\}  \textsf{ rvs}  \ast r_a \mapsto_{r} \; \{q_2\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{ v} \}_{\textsf{rtv}}\;\overline{ is}  

@@

  \{P \ast \mathcal{I}\textsf{ASpace}\ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{ iv} \ast r_s \mapsto_{r} \;\{q_1\}  \textsf{ rvs}   \ast r_a \mapsto_{r} \; \{q_2\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{ rvs} \}_{\textsf{rtv}}

@@

  \{[\textsf{rtv}](P \ast \mathcal{I}\textsf{ASpace})\ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{ iv + 4} \ast \mathcal{I}\textsf{ASpace} \ast R\ast r_s \mapsto_{r} \;\{q\}  \textsf{ rvs}  \}_{\textsf{rvs}} \;\overline{is}

@@

  \{P \ast \mathcal{I}\textsf{ASpace} \ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{ iv} \ast [\textsf{rvs}](R \ast\mathcal{I}\textsf{ASpace})\ast r_s \mapsto_{r}\; \{q\}  \textsf{ rvs}   \}_{\textsf{rtv}} \;

@@

\subsubsection{Accessing Virtual Addresses}
Figure \ref{fig:wpdamd} includes two  rules for accessing memory at an address stored in a register $r_a$. 
\add{Setting aside $P$, $\mathcal{I}\textsf{ASpace}$, and the instruction pointer \lstinline|rip|,}
\del{Ultimately, any memory access needs to ensure the relevant address translation would succeed,
which can be ensured by what we informally call the page-table-walk points-to collection
($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ in Figure ??). }
\TirNameStyle{WriteToRegFromVirtMem} and \TirNameStyle{WriteToVirtMemFromReg}
\del{each use a virtual-pointsto assertion ($\textsf{vaddr} \mapsto_{\textsf{v}} \textsf{v}$),
and }
are nearly-standard (assembly) separation logic rules for memory accesses~\add{\cite{Chlipala2013Bedrock,ni2007contexts}}.
\add{For example, \textsc{WriteToRegFromVirtMem}'s specification
reflects that it reads from the (virtual) memory address \textsf{vaddr} stored in the address
register $\textsf{r}_a$ --- and thus requires register points-to and virtual points-to assertions describing
that relationship and the assumed value \textsf{v} in memory in its precondition (the precondition of the rule's
conclusion). 
It reflects the load (\lstinline|mov|) of that memory value into the destination register $\textsf{r}_d$, with
the updated register points-to in the precondition for $\overline{is}$.
$P$ describes framed resources, which are passed along to the precondition of subsequent instructions,
as in any system of Hoare doubles~\cite{Chlipala2013Bedrock,ni2007contexts}.
\textsc{WriteToVirtMemFromReg} is analogous for writing to memory.
}
\add{There are only two changes specific to our approach.}
\looseness=-1

\replace{However, }{First,}
because we split the physical resources for the page table walk from the
virtual points-to itself (\replace{in order to permit the physical page tables to be freely modified
as long as they preserve virtual-to-physical translations}{per the discussion of Section \ref{sec:sharingpages}}), the rule requires $\mathcal{I}\textsf{ASpace}$
for the current address space to be carried through.
The soundness proofs for these rules extract
the token ($\fracghostmaptoken{\delta}{\vaddr}{\paddr}{\qfrac}$) from the virtual points-to,
use that to extract the physical page-table-traversal points-to collection describing
the page table walk for the relevant address ($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$)
from the invariant ($\mathcal{I}\mathsf{ASpace}$), prove that the page table walk succeeds
and that memory or registers are updated appropriately, before re-packing the invariant and virtual points-to resources.
\looseness=-1

@@

\subsubsection{Updating \lstinline|cr3|} 
Unlike other rules, \TirNameStyle{WriteToRegCtlFromRegModal} updates the root address of the 
address space determining the validity of resources, from $\rtv$ before the
\lstinline|mov| to $\textsf{rvs}$ afterwards. The global effects of this rule are reflected in moving
\del{bare} assertions \add{for the current address space ($P$ and $\mathcal{I}\mathsf{ASpace}$)} under an other-space modality for \add{the initial
(outgoing) address space} $\rtv$, and moving the new address space's assertions out of
the corresponding modality \add{(since after the \lstinline|mov|, those will hold in the
new current address space)}.

>>>>

  \begin{figure*}
  \footnotesize
\vspace{-1em}
\centerline{$
\begin{array}{l}
   I\textsf{ASpace}(\ptablestore,m)\stackrel{\triangle}{=} \textsf{ASpace\_Lookup}(\ptablestore,m) \ast 
  \bigast{(\vaddr, \textsf{pa})\in \ptablestore}{\exists\;(\textsf{l4e l3e l2e, l1e, pa})\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\vaddr\textsf{, l4e, l3e, l2e, l1e, pa})} \\
  \textsf{ where } 
   \textsf{ASpace\_Lookup} (\ptablestore,m) \stackrel{\triangle}{=} \lambda\textsf{ cr3val} \ldotp \; \exists \gammaPred \; \ldotp \ulcorner m \; !!\; \textsf{cr3val} = \textsf{Some } \gammaPred \urcorner \ast
    %\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}
    \ptableabswalk{\delta,\theta}
\end{array}
$}
\vspace{-1em}
\caption{Per-address-space invariant with a fixed global map of address space names $m$}
  \label{fig:peraspaceinvariant}
\vspace{-1em}
  \end{figure*}

We place the authorative ownership of the ghost \add{map} translation $\mathcal{A}\textsf{PTableWalk}$ in a per-address-space invariant
$ I$\textsf{ASpace} (Figure \ref{fig:peraspaceinvariant}), 
\replace{$ I$\textsf{ASpace} alone allows}{allowing} changes to the page tables
that preserve overall virtual-to-physical translations \add{in isolation},
\add{and also allowing changes to specific the virtual-to-physical translations}
\replace{W}{w}hen combined with the
\replace{fragment}{token} stored in the \add{relevant} virtual points-to (Figure \ref{fig:virtualpointstosharing}).
\del{changes in the virtual-to-physical translations become possible without the need to track all virtual points-to assertions.}
\looseness=-1

% \todo[inline,color=cyan]{Explain $\delta{s}$ (Iris ghost name) vs $m$ (logical contents of ghost map) in next 2 paragraphs}
% \todo[inline]{This next paragraph below explains details, but should first explain the big picture: the current address space
% is identified by a paddr, so to state the invariant for the address space named by that paddr we need to look up
% what invariants should hold, then assert that those invariants do hold.}
\add{We must also ensure that different address spaces can have independent ghost maps ---
which we resolve with an additional unique global ghost map (with ghost name $\delta{s}$) from address-space identifiers (page table roots
whose values are manipulated by the kernel code) to
the \textsc{Iris} ghost name for that address space's ghost map.
In Figure \ref{fig:virtualpointstosharing}, the extra ghost map token for $\delta{s}$ asserts that $\delta$ --- which is exisentially
quantified --- is the correct ghost name for the current address space. That is then the ghost map named
in the ghost virtual-to-physical translation token of Figure \ref{fig:virtualpointstosharing}.
}
\del{In Figure ??,
$\theta$ is the logical map from virtual addresses to the physical addresses they should translate to, 
for the \emph{current} address space, corresponding to the  currently installed page tables (the ones
indicated by \texttt{cr3}). In Figure ??, the existentially quantified $\delta$
is the ghost name for this map (again, for the current address space).
Because our logic is the first to address the existence of multiple address spaces,
it must ensure that $\theta$ actually corresponds to the intended ghost map for the current address space.
This requires looking up the ghost name (i.e., $\delta$) for the current address space,
which is handled by $m$ --- another logical map (tied to ghost state shortly)
from various page table roots to ghost names for the per-address-space ghost maps discussed above.
}
\add{
Just as the ghost name $\delta$ names the ghost map with contents $\theta$,
$\delta{s}$ names a ghost map, whose contents appear as $m$ in Figure \ref{fig:peraspaceinvariant} (the association of $\delta{s}$ to $m$
is a global invariant not shown).
}
$ I\textsf{ASpace}(\theta,m)$ then \add{performs 3 roles:
it associates the current address space's root with an appropriate \textsc{Iris} ghost name $\delta$;
it tracks authoritatively that $\delta$'s logical contents match $\theta$; and it}
stores the physical resources for the current address space mappings \add{(via the iterated $\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$)}.
\del{ensuring that the current address space is valid (has an entry in $m$ whose corresponding
authoritative map matches $\theta$), and asserting ownership of the appropriate fractional ownership
of the physical page table walk for each virtual-to-physical translation in $\Theta$ (for the current address space).}

@@

% Figure \ref{fig:logicaladdrspace} depicts the relationships between these pieces, for a single
% address space.
% The invariant for the currently active address space (solid round square labelled as 
% $ I$\textsf{ASpace} in Figure \ref{fig:logicaladdrspace}) asserts authorative ownership (i.e. 
% update capability), $\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$, of the ghost map $\Theta$
% describing virtual-to-physical address translations
% -- shown as a solid-round-head arrow to $\mathcal{A}\textsf{PTableWalk}$.
% Each virtual points-to assertion (dashed round square labelled as \textsf{Virtual PointsTo}
%  in Figure \ref{fig:peraspaceinvariant})
% asserts fragmental ownership of the ghost map $\Theta$, $\sumwalkabs\vaddr\qfrac\paddr$,
% shown via the dashed-diamond-head arrow to $\mathcal{A}\textsf{PTableWalk}$. Specifically, it asserts that
% the virtual address the virtual points-to assertion concerns corresponds to some physical address.
% There exists only one persistent authorative ownership 
% ($\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$) which collects the fragmental 
% ghost page-table-walk mapping ($\sumwalkabs\vaddr\qfrac\paddr$),
%  shown as double-ended solid arrow 1 to N imposing the update protocol.

@@

% \paragraph{From A Single Address Space to Many}
% In principle the resources from each individual address space should be collected into a single
% shared invariant, and for each memory access,
% a fragment of this corresponding to $ I\textsf{ASpace}(\Theta,m)$
% for the current address space should be extracted from this global resource, used to prove correctness of the
% memory access, and put back.
% In this paper we focus on the middle section, explicity identifying resources for each
% address space. The reason for this is that in practice, this global resource is also
% the place where kernel-specific assumptions, such as guaranteeing that certain virtual address range
% was mapped in all address spaces, would be enforced. This paper focuses on the
% reasoning principles behind the virtual memory access, and we leave the use of this within a larger
% kernel to future work. We do, however, deal with the existence of multiple address spaces in examples (Section \ref{sec:experiment}).

@@

    P \ast  I\textsf{ASpace}\ast  \textsf{rip} \mapsto_{\textsf{r}} \; {\textsf{iv} + \textsf{MovLen}(\textsf{r}_d,[\textsf{r}_a])} \ast \arcr

@@

  \{P \ast  I\textsf{ASpace}\ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{ iv} \ast r_d \mapsto_{r}  \textsf{ rvd} \ast r_a \mapsto_{r} \;\{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{ v} \}_{\textsf{rtv}}\;

@@

  \{P \ast  I\textsf{ASpace}\ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{ iv} + \textsf{MovLen}(\textsf{r}_d,[\textsf{r}_a])  \ast r_s \mapsto_{r}\;\{q_1\}  \textsf{ rvs}  \ast r_a \mapsto_{r} \; \{q_2\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{ v} \}_{\textsf{rtv}}\;\overline{ is}  

@@

  \{P \ast  I\textsf{ASpace}\ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{ iv} \ast r_s \mapsto_{r} \;\{q_1\}  \textsf{ rvs}   \ast r_a \mapsto_{r} \; \{q_2\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{ rvs} \}_{\textsf{rtv}}

@@

  \{[\textsf{rtv}](P \ast  I\textsf{ASpace})\ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{ iv + 4} \ast  I\textsf{ASpace} \ast R\ast r_s \mapsto_{r} \;\{q\}  \textsf{ rvs}  \}_{\textsf{rvs}} \;\overline{is}

@@

  \{P \ast  I\textsf{ASpace} \ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{ iv} \ast [\textsf{rvs}](R \ast I\textsf{ASpace})\ast r_s \mapsto_{r}\; \{q\}  \textsf{ rvs}   \}_{\textsf{rtv}} \;

@@

\subsubsection{Accessing Virtual Addresses}
Figure \ref{fig:wpdamd} includes two  rules for accessing memory at an address stored in a register $r_a$. 
\add{Setting aside $P$, $ I\textsf{ASpace}$, and the instruction pointer \lstinline|rip|,}
\del{Ultimately, any memory access needs to ensure the relevant address translation would succeed,
which can be ensured by what we informally call the page-table-walk points-to collection
($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$ in Figure ??). }
\TirNameStyle{WriteToRegFromVirtMem} and \TirNameStyle{WriteToVirtMemFromReg}
\del{each use a virtual-pointsto assertion ($\textsf{vaddr} \mapsto_{\textsf{v}} \textsf{v}$),
and }
are nearly-standard (assembly) separation logic rules for memory accesses~\add{\cite{Chlipala2013Bedrock,ni2007contexts}}.
\add{For example, \textsc{WriteToRegFromVirtMem}'s specification
reflects that it reads from the (virtual) memory address \textsf{vaddr} stored in the address
register $\textsf{r}_a$ --- and thus requires register points-to and virtual points-to assertions describing
that relationship and the assumed value \textsf{v} in memory in its precondition (the precondition of the rule's
conclusion). 
It reflects the load (\lstinline|mov|) of that memory value into the destination register $\textsf{r}_d$, with
the updated register points-to in the precondition for $\overline{is}$.
$P$ describes framed resources, which are passed along to the precondition of subsequent instructions,
as in any system of Hoare doubles~\cite{Chlipala2013Bedrock,ni2007contexts}.
\textsc{WriteToVirtMemFromReg} is analogous for writing to memory.
}
\add{There are only two changes specific to our approach.}
\looseness=-1

\replace{However, }{First,}
because we split the physical resources for the page table walk from the
virtual points-to itself (\replace{in order to permit the physical page tables to be freely modified
as long as they preserve virtual-to-physical translations}{per the discussion of Section \ref{sec:sharingpages}}), the rule requires $ I\textsf{ASpace}$
for the current address space to be carried through.
The soundness proofs for these rules extract
the token ($\fracghostmaptoken{\delta}{\vaddr}{\paddr}{\qfrac}$) from the virtual points-to,
use that to extract the physical page-table-traversal points-to collection describing
the page table walk for the relevant address ($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}$)
from the invariant ($ I\mathsf{ASpace}$), prove that the page table walk succeeds
and that memory or registers are updated appropriately, before re-packing the invariant and virtual points-to resources.
\looseness=-1

@@

\subsubsection{Updating \lstinline|cr3|} 
Unlike other rules, \TirNameStyle{WriteToRegCtlFromRegModal} updates the root address of the 
address space determining the validity of resources, from $\rtv$ before the
\lstinline|mov| to $\textsf{rvs}$ afterwards. The global effects of this rule are reflected in moving
\del{bare} assertions \add{for the current address space ($P$ and $ I\mathsf{ASpace}$)} under an other-space modality for \add{the initial
(outgoing) address space} $\rtv$, and moving the new address space's assertions out of
the corresponding modality \add{(since after the \lstinline|mov|, those will hold in the
new current address space)}.
